Convective penetration is set by the flux and dissipation, not the stiffness

### 2021-05-29 manuscript/ms.tex
good-enough draft to send around

\begin{abstract}
Convection is a crucial heat transport mechanism and excitation mechanism in planets and stars.
While parameterizations like mixing length theory adequately describe convection in bulk convection zones, the behavior of convective motions near and beyond the Schwarzschild-stable convective boundary are not well understood.
In this paper, we examine a simplified Boussinesq model of stellar convection with a radiative flux.
We derive a ``penetration parameter'' $\mathcal{P}$ which compares how quickly the radiative gradient deviates from the adiabatic on either side of the convective boundary.
In line with \citet{zahn1991}, we predict that the extend of the adiabatically stratified penetrative layer is strongly related to the magnitude of $\mathcal{P}$.
We perform 3D numerical simulations using Dedlaus to test this theory, and find that the penetrative region strongly depends on the flux-based $\mathcal{P}$ and only weakly depends on the degree of turbulence in the flows or on the stiffness of the convective interface.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20\% of a mixing length.
We briefly examine a MESA solar model in which the bottom boundary of the convection zone is set according to our theory, and discuss the possible implications and future paths necessary for these findings.
\end{abstract}
\keywords{UAT keywords}

@@

Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}, such as the classic Mixing Length Theory \citep{bohm-vitense1958}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the extent of the extent of the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.

@@

A few flux-based theories of convective penetration have been historically considered.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

@@

\subsection{Equations}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
= \alpha g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution: \citet{roxburgh1989}'s integral constraint,
\begin{equation}
\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
\label{eqn:ke_averages}
\end{equation}
where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.

We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
Following Eqn.~\ref{eqn:ke_averages}, we write
\begin{equation}
\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{\alpha g} \angles{|\vec{\omega}|^2}.
\label{eqn:flux_breakup}
\end{equation}
Rearranging, we retrieve 
\begin{equation}
\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
\qquad\rm{with}\qquad
f \equiv \frac{(L_s + \delp)}{\alpha g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
\label{eqn:preliminary_flux_ratio}
\end{equation}
where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics (the viscous dissipation), quantified by $f$.
We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.

\subsection{A flux-based penetration argument}
\citet{zahn1991} and Eqn.~\ref{eqn:preliminary_flux_ratio} suggest that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates some distance $\delp$ above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the PZ.
This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
Defining the radiative gradient $\grad_{\rm{rad}} = \Ftot/k$, we can write the PZ convective flux
\begin{equation}
\overline{\Fconv}|_{\rm{PZ}} = \Ftot - \overline{\Frad} = k(\gradrad - \gradad).
\label{eqn:fconv_pz}
\end{equation}
Within the penetrative region, $\gradad > \gradrad$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv}|_{\rm{PZ}} < 0$.

@@

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{\alpha g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

@@

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper study simulations with a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H$ for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

@@

In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) from Case I (discontinuous $k$) simulations.
In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is roughly the same size as the nominal convection zone.
We find that the value of $\mP_D$ is the primary parameter whose value modifies the height of the convection zone.
While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
This signifies that $f$, and thus the viscous dissipation, is smaller in 2D than in 3D; we speculate that this is a consequence of the inverse turbulent cascade in 2D.

>>>>

\begin{abstract}
Convection is a crucial heat transport and dynamical excitation mechanism in stars.
Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
In this paper we examine how convective motions mix the background thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
We use a simplified Boussinesq model of stellar convection with a radiative flux.
We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20-30\% of a mixing length.
We present a MESA solar model which uses our parameterization of convective penetration, and find that the base of the solar convection zone extends by (X amount for some choice of parameters).
We briefly discuss future experiments which could verify and extend these results to stellar contexts.
\end{abstract}
\keywords{UAT keywords}

@@

Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.

@@

A few flux-based theories of convective penetration have been historically considered.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

@@

\subsection{Equations}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution: \citet{roxburgh1989}'s integral constraint,
\begin{equation}
|\alpha| g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
\label{eqn:ke_averages}
\end{equation}
where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.

We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
Following Eqn.~\ref{eqn:ke_averages}, we write
\begin{equation}
\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
\label{eqn:flux_breakup}
\end{equation}
Rearranging, we retrieve 
\begin{equation}
\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
\qquad\rm{with}\qquad
f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
\label{eqn:preliminary_flux_ratio}
\end{equation}
where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.

\subsection{A flux-based penetration argument}
\citet{zahn1991} and Eqn.~\ref{eqn:preliminary_flux_ratio} suggest that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates some distance $\delp$ above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the PZ.
This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
Defining the radiative gradient $\gradrad = \Ftot/k$, we can write the PZ convective flux
\begin{equation}
\overline{\Fconv}|_{\rm{PZ}} = \Ftot - \overline{\Frad} = k(\gradrad - \gradad).
\label{eqn:fconv_pz}
\end{equation}
Within the penetrative region, $\gradad > \gradrad$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv}|_{\rm{PZ}} < 0$.

@@

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

@@

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

@@

In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) from Case I (discontinuous $k$) simulations.
In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is roughly the same size as the nominal convection zone.
%We find that the value of $\mP_D$ is the primary parameter whose value modifies the extent of the PZ.
While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
This signifies that $f$, and thus the viscous dissipation, is smaller in 2D than in 3D; we speculate that this is a consequence of the inverse turbulent cascade in 2D.
